Seagrass mapping and monitoring along the coasts of Crete, Greece

### 2011-01-16 MScDiplom_Lemenkova.tex
formatted LaTeX document

@@

\begin{wrapfigure}{r}{0.4\textwidth}
\centering
\includegraphics[scale=0.15]{Fig-1-7.jpg}
\caption{Scheme of matte structure of
P.Oceanica.\\ Source \cite{Pergent90}\label{Pergent90}}
\label{fig:7}
\end{wrapfigure}

@@

\subsection{Google Earth aerial imagery for seagrass mapping}
Apart from the satellite imagery, the aerial photographs from the Google Earth provide
a powerful tool for seagrass mapping, because they are important, reliable, detailed
and up-to-date source of imagery.
\begin{wrapfigure}{r}{0.5\textwidth}
\centering
\includegraphics[scale=0.27]{Fig-22.jpg}
\caption{Capturing aerial imagery from the Google Earth: grabbing process}
\label{fig:22}
\end{wrapfigure}

@@

\subsection{Review of the collected data}
The remote sensing imagery were collected for the Crete island area covering the research period and
area, enabling the field data to be used for the calibration and validation. The available aerial and
satellite imagery are commonly used for the mapping of seagrass landscapes and their application is
proven by various research papers. The imagery include satellite multi-spectral imagery (Landsat-TM,
ETM+) and aerial imagery from the Google Earth.
The overview of the collected data enables to summarize their following types:
\begin{itemize}
\item[] 1. Optical spectra of P.oceanica, carbonate sand, seawater with sediments and seawater measured in aquarium tank, without sediments, at different environmental conditions (e.g., Fig. \ref{fig:23})
\item[]2. Aerial imagery from the \href{http://www.google.com/earth/index.html}{Google Earth}
\item[]3. Satellite images from various open sources (e.g. Landsat, Tab \ref{tab:20}) (previews: Fig. \ref{fig:68})
\item[]4. Results of underwater videometric measurements of the Olympus cameras made during the ship route
\end{itemize}
The available satellite imagery (Fig.\ref{fig:68}) and aerial images are read into the ArcGIS project.
The available broadband and hyperspectral remote sensing data are used for the mapping of the
seagrass in shelf areas no deeper than 4.0 meters, for the environmental monitoring in order to detect
the dynamics in changes of the seagrass distribution along Crete during the past 10 years using
different satellite images for 2000-2010.
The spatial resolution of Landsat ETM+ image is 30 m in the visible and near infrared bands (bands
1-5 and 7); the spatial resolution of ASTER 15 m for the visible and near-infrared bands. IKONOS
acquires data in 3 visible channels and NIR, with spatial resolution of 1-4 meters. ASTER and
IKONOS images are suggested to be included as soon as available, in addition to the Landsat. The
research includes fieldwork in-situ measurements of the seagrass distribution along the northern and
south-eastern coasts of Crete in chosen locations.\\
The optical measurements of the irradiance and radiance of the sea water and bottom cover types of
the seafloor have been received by the means of the optical sensors Trios-RAMSES Hyperspectral
UVA/UVB Irradiance Sensor and RAMSES-ARC Hyperspectral UV-VIS Radiance Sensor (Fig. \ref{fig:10}), both adjusted for the measurements of the irradiance and radiance (see Appendices: Tab. \ref{tab:18}, Tab. \ref{tab:19}).
The highest measured values are located in the diapason of 410-730 nm for the water irradiance (Fig. \ref{fig:49}) and 430-650 for the water radiance (Fig.\ref{fig:47}). 
Afterwards, the measured values of the
radiance and irradiance, respectively, have been used for the computation of the spectral reflectance
properties of the sea water and bottom cover types (Fig.\ref{fig:23}). The spectral range of radiance
cover diapason of 320-950 nm, and ittadiance measurements are covered in the interval of 280-500
nm, which is suitable for a characteristics of seagrass reflectance.
Different curves on the reflectance, radiance and irradiance graphs for example, on Fig.\ref{fig:43}, or \ref{fig:45}, enlarged) represent several series of
the measurements. The values of the spectral reflectance are received from the
computations of these values using Excel mathematical formulae. The graphs shown on Fig.\ref{fig:47}, Fig. \ref{fig:48}, Fig. \ref{fig:49} display values of the radiance and irradiance of the sea water in Agia Pelagia, with and without sediments and suspended particles, respectively. Graph on Fig \ref{fig:44} displays statistuical analysis of the measured sets of observations, i.e. shows the midspread of the statistical quartiles (Q1-Q3), mean and extreme values.
\begin{figure}[h]
\centering
\includegraphics[scale=0.5]{GNU-17.jpg}
\caption{Optical properties of the sea water with sediments, measured in aquarium tank. Agia Pelagia district, Crete}
\label{fig:23}
\end{figure}

@@

\begin{table}[htbp]
\rowcolors{1}{LightSteelBlue}{Honeydew}
\caption{Results of the statistical analysis of spectral reflectance of \textbf{P.oceanica}, with average values (for sets 1 - 350). Generalisation up to step 20 nm}
\begin{center}
%\rowcolors{1}{lightgray}{white}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Wavelength, nm & mean & Q1 & min & Q3 & max & median \\ \hline
\textbf{318.23354} & 0.030467 & 0.038907 & 0.029764 & 0.069762 & 0.116100 & 0.048984 \\ \hline
\textbf{338.29900} & 0.033560 & 0.043030 & 0.032847 & 0.076252 & 0.128290 & 0.054334 \\ \hline
\textbf{358.37932} & 0.039897 & 0.051320 & 0.039131 & 0.091143 & 0.154409 & 0.066354 \\ \hline
\textbf{378.47247} & 0.045786 & 0.058849 & 0.045039 & 0.105993 & 0.177150 & 0.078339 \\ \hline
\textbf{398.57640} & 0.052346 & 0.066859 & 0.051625 & 0.122328 & 0.201038 & 0.091905 \\ \hline
\textbf{418.68905} & 0.058942 & 0.074842 & 0.058240 & 0.138984 & 0.226028 & 0.106207 \\ \hline
\textbf{438.80838} & 0.070690 & 0.089761 & 0.069999 & 0.167825 & 0.267712 & 0.130580 \\ \hline
\textbf{458.93235} & 0.080107 & 0.102089 & 0.079392 & 0.191424 & 0.304933 & 0.149762 \\ \hline
\textbf{479.05891} & 0.086278 & 0.110348 & 0.085546 & 0.207940 & 0.332934 & 0.162881 \\ \hline
\textbf{499.18600} & 0.098498 & 0.126592 & 0.097689 & 0.239161 & 0.380603 & 0.188192 \\ \hline
\textbf{519.31159} & 0.110222 & 0.143976 & 0.109022 & 0.265948 & 0.421370 & 0.210237 \\ \hline
\textbf{539.43363} & 0.125694 & 0.166156 & 0.124310 & 0.302678 & 0.475842 & 0.240492 \\ \hline
\textbf{559.55006} & 0.131844 & 0.175865 & 0.130257 & 0.319385 & 0.503907 & 0.253726 \\ \hline
\textbf{579.65885} & 0.121915 & 0.166084 & 0.120186 & 0.302078 & 0.485661 & 0.237873 \\ \hline
\textbf{599.75794} & 0.077236 & 0.111113 & 0.075669 & 0.200557 & 0.343876 & 0.154016 \\ \hline
\textbf{619.84529} & 0.057038 & 0.085386 & 0.055588 & 0.154781 & 0.281737 & 0.117003 \\ \hline
\textbf{639.91885} & 0.050841 & 0.077438 & 0.049432 & 0.141810 & 0.265181 & 0.106188 \\ \hline
\textbf{659.97657} & 0.038118 & 0.059971 & 0.036997 & 0.110774 & 0.223366 & 0.082411 \\ \hline
\textbf{680.01641} & 0.032892 & 0.052265 & 0.032012 & 0.095789 & 0.198389 & 0.071686 \\ \hline
\textbf{700.03633} & 0.034756 & 0.058426 & 0.033643 & 0.101504 & 0.215413 & 0.075789 \\ \hline
\textbf{720.03426} & 0.026287 & 0.047084 & 0.025162 & 0.082940 & 0.193535 & 0.061184 \\ \hline
\textbf{740.00817} & 0.009740 & 0.022355 & 0.010145 & 0.042861 & 0.132244 & 0.029414 \\ \hline
\textbf{759.95601} & 0.008651 & 0.020234 & 0.009191 & 0.039371 & 0.128165 & 0.026558 \\ \hline
\textbf{779.87573} & 0.006019 & 0.014157 & 0.006397 & 0.028320 & 0.100314 & 0.019322 \\ \hline
\textbf{799.76528} & 0.008607 & 0.020030 & 0.009050 & 0.037323 & 0.118123 & 0.026535 \\ \hline
\textbf{819.62263} & 0.008777 & 0.020295 & 0.009288 & 0.037598 & 0.118055 & 0.026799 \\ \hline
\textbf{839.44571} & 0.002562 & 0.008010 & 0.002864 & 0.017472 & 0.076515 & 0.011432 \\ \hline
\textbf{859.23249} & 0.002653 & 0.006921 & 0.002897 & 0.016121 & 0.070377 & 0.009889 \\ \hline
\textbf{878.98091} & 0.002327 & 0.008080 & 0.002821 & 0.018625 & 0.082462 & 0.011617 \\ \hline
\textbf{898.68893} & 0.004077 & 0.013098 & 0.004709 & 0.031217 & 0.101146 & 0.019767 \\ \hline
\textbf{918.35451} & 0.006215 & 0.020162 & 0.007229 & 0.045213 & 0.199711 & 0.029950 \\ \hline
\textbf{937.97559} & 0.005783 & 0.026132 & 0.007307 & 0.065475 & 0.195072 & 0.040848 \\ \hline
\textbf{951.03058} & 0.002296 & 0.026581 & 0.002380 & 0.067924 & 0.265845 & 0.041463 \\ \hline
\end{tabular}
\end{center}
\label{fig:5}
\end{table}

@@

\begin{figure}[h]
\centering
\includegraphics[scale=0.30]{Fig-30.jpg}
\caption{Main interface of WASI water color spectral simulation: \\ Spectral reflectance of \textit{P.oceanica} and silt at 0.5-
4.0m}
\label{fig:30}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\subfloat [Concentration of Gelbstoff at depths 0.5 – 8.0 m]{\label{fig:31a}\includegraphics[width=0.4\textwidth]{Fig-31a.jpg}}
	\subfloat [Bottom reflectance at depth 0.5-4.0 meters]{\label{fig:31b}\includegraphics[width=0.4\textwidth]{Fig-31b.jpg}}
	\caption{Sea water physical properties, modelled by WASI}
	\label{fig:31}
\end{figure}
\paragraph{Model parameters: depth and bottom cover fraction}
Although seagrass \textit{P.oceanica} can be found until depth limits down to 40 m depth (Hartog
1970), the most preferrable limits of its distribution in the Mediterranean Sea are shallow waters until
4 meters of depth.

\begin{table}
\rowcolors{1}{Aquamarine}{Azure}
\caption{Model-specific parameters of water WASI adjusted to simulate environment of the Mediterranean Sea along Crete}
\centering
%\rowcolors{1}{lightgray}{white}
% \scalebox{0.7}
  \begin{tabular}{|  p{2cm} | p{6cm} | p{25mm} | }
    \hline
    \textbf{Parameter, WASI} & \textbf{Name and description} & \textbf{Values} \\ \hline\hline
    C-L & Concentration of large suspended particles & 8 \\ \hline
   C(i), i=0..5 & Concentration of Phytoplankton & 0.035 -0.089 ug -l \\ \hline
    bbS & Specific backscattering for small particles & 0.005 m2g-1 \\ \hline
   T-W & Temperature of water & 17-25 °C \\ \hline
    n & Exponent of Backscattering by small particles & 0.005 m2g-1 \\ \hline
    Q &Anisotropy factor of upwelling radiation ("Q-factor") & 5.00 \\ \hline
    sigma-L & Reflection factor of sky radiance & 0.0201 \\ \hline
    b1 & Backscattering coefficient of saline waters & 0.00144 m-1 \\ \hline
    λ0 & Reference Wavelength for Gelbstoff absorption & 440 \\ \hline
    sun & Sun zenith angle & 45.0 \\ \hline
    zB & Bottom depth & 4.00 \\ \hline
   f(i), i=0...5 & Areal fraction of bottom surface type number n & 01/10/10 \\ \hline
    K0 & Coefficient of Attentuation & 1.0546 \\ \hline
   view & Viewing angle (0 = nadir) & 0\\ \hline
    C-X & Concentration of non-chlorophyllous particles (absorption at λ0) & 0 \\ \hline
   λS & Reference wavelength for scattering of small particles & 500 \\ \hline
    C-S & Concentration of small suspended particles & 0 \\ \hline
   S & Exponent of Gelbstoff absorption & 0.0140 \\ \hline
    C-Y & Concentration of Gelbstoff (absorption at λ0) & 0.400 \\ \hline
    Bn & BDRF of bottom reflectance (sand) & 0.318 sr -1\\
    \hline
  \end{tabular}
   \label{tab:3}
\end{table}

@@

\paragraph{Spectral discrimination of \textit{P.oceanica}}
The patches of white sandy bottoms of the seafloor, studied in the fieldwork in Ligaria beach, are
much brighter than mattes of P.Oceanica ((Fig.\ref{fig:64}): seafloor types in Ligaria), which can be clearly seen
at the graph comparing values of the spectral reflectance of the carbonate sand (Fig.\ref{fig:65}) and that of P.
oceanica (Fig.\ref{fig:62}).

The graph is received in excel spreadsheet using mean values of spectral reflectances of
sand (Fig.\ref{fig:34}) and seagrass (Fig.\ref{fig:32}), respectively, which have been calculated from measurements of radiance and
irradiance received in Agia Pelagia bay.

@@

Finally we
analysed 400 datasets made on two different data. 

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{GNU-13.jpg}
\caption{Multiplot of spectral reflectance of P.oceanica. Series 1-100. Shown midspread of the statistical quartiles Q1 and Q3 (vertical dashes) and
mean value within the range (red bold dots). Gnuplot visualization­}
\label{fig:35}
\end{center}
\end{figure}
\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{GNU-16.jpg}
\caption{Multiplot of spectral reflectance of carbonate sand. Series 1-75. Shown midspread of the statistical quartiles Q1 and Q3 (vertical dashes) and
mean value within the range (red bold dots). Gnuplot visualization­}
\label{fig:36}
\end{center}
\end{figure}

@@

\begin{table}[htbp]
\rowcolors{1}{Ivory}{GhostWhite}
\caption{Model summary of the \textit{regression} analysis: curve estimation and ANOVA table tested for single observations within one measurement set: spectral reflectance of \textbf{P.oceanica}. SPSS}
\label{tab:5}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline\hline
\textbf{R} & \textbf{R square} & \textbf{Adjusted R square} & \textbf{Std. Error of the Estimate} \\ \hline\hline
.277 1 & .077 & .068126692 & .462 \\ \hline
\end{tabular}
\end{center}
the independent variable is wavelength. 
\label{fig:5}
\end{table}

\begin{table}[htbp]
\rowcolors{1}{Ivory}{GhostWhite}
\caption{\textit{ANOVA} table: exponential curve estimation in the regression analysis, tested for single observations within one measurement set: spectral reflectance of \textbf{P.oceanica}. SPSS}
\label{tab:6}
\begin{center}
\begin{tabular}{|c|c|c|c| c|c|}
\hline\hline
& \textbf{Sum of squares} & \textbf{df} & \textbf{Mean Square} & F & Sig.\\ \hline\hline
Regression & 1.810 & 1 & 1.810 & 8.477 & .004\\ \hline
Residual & 21.781 & 102 & .214 & & \\ \hline
Total & 23.592 & 103 & & & \\ \hline
\end{tabular}
\end{center}
the independent variable is wavelength. 
\label{fig:5}
\end{table}

\begin{table}[htbp]
\rowcolors{1}{Ivory}{GhostWhite}
\caption{Coefficients of the \textit{regression analysis} (exponential curve estimation) of the spectral reflectance of \textbf{P.oceanica}. SPSS}
\label{tab:7}
\begin{center}
\begin{tabular}{| c | c | p{2cm}| c | c | c |}
\hline\hline
& \multicolumn{2}{|c|}{Unstandardized Coefficients}\\
\cline{2-3}
& B & Std.Error & Stand. Coef. Beta & t & Sig.\\ \hline\hline
wavelength & -.001 & .000 & -.277 & -2.912 & .004 \\ \hline
constant & .464 & .121 & & 3.821 & .000 \\ \hline
\end{tabular}
\end{center}
a. The underlying process assumed is independence (white noise).\\
b. Based on the asymptotic chi-square approximation.
\label{fig:5}
\end{table}
\pagebreak

\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.20]{GNU-Stat-M-401-420.jpg}
\caption{Fragment of the statistical analysis of the P.oceanica reflectance. Example of data set 401-420. 
Visualisation of the measured data together with styatistical values: interquartile ranging, medians, means.}
\label{fig:46}
\end{center}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[scale=0.25]{GNU-Radiance_Bezier.jpg}
\caption{Radiance of the seawater with sediments. Measured in 
aquarium tank. Bezier Interpolation}
\label{fig:47}
\end{figure}

>>>>

\vspace{5em}

@@

\begin{wrapfigure}{r}{0.4\textwidth}
	\centering
	\includegraphics[scale=0.15]{Fig-1-7.jpg}
	\caption{Scheme of matte structure of \textit{	P.Oceanica}.\\ Source \cite{Pergent90}\label{Pergent90}}
	\label{fig:7}
\end{wrapfigure}

@@

\subsection{Google Earth aerial imagery for seagrass mapping}
Apart from the satellite imagery, the aerial photographs from the Google Earth provide
a powerful tool for seagrass mapping, because they are important, reliable, detailed
and up-to-date source of imagery.

\begin{wrapfigure}{r}{0.5\textwidth}
	\centering
	\includegraphics[scale=0.27]{Fig-22.jpg}
	\caption{Capturing aerial imagery from the Google Earth: grabbing process}
	\label{fig:22}
\end{wrapfigure}

@@

\subsection{Review of the collected data}
The remote sensing imagery were collected for the Crete island area covering the research period and
area, enabling the field data to be used for the calibration and validation. The available aerial and
satellite imagery are commonly used for the mapping of seagrass landscapes and their application is
proven by various research papers. The imagery include satellite multi-spectral imagery (Landsat-TM,
ETM+) and aerial imagery from the Google Earth.
The overview of the collected data enables to summarize their following types:
\begin{itemize}
	\item[] 1. Optical spectra of P.oceanica, carbonate sand, seawater with sediments and seawater measured in aquarium tank, without sediments, at different environmental conditions (e.g., Fig. \ref{fig:23})
	\item[]2. Aerial imagery from the \href{http://www.google.com/earth/index.html}{Google Earth}
	\item[]3. Satellite images from various open sources (e.g. Landsat, Tab \ref{tab:20}) (previews: Fig. \ref{fig:68})
	\item[]4. Results of underwater videometric measurements of the Olympus cameras made during the ship route
\end{itemize}
The available satellite imagery (Fig.\ref{fig:68}) and aerial images are read into the ArcGIS project.
The available broadband and hyperspectral remote sensing data are used for the mapping of the
seagrass in shelf areas no deeper than 4.0 meters, for the environmental monitoring in order to detect
the dynamics in changes of the seagrass distribution along Crete during the past 10 years using
different satellite images for 2000-2010.
The spatial resolution of Landsat ETM+ image is 30 m in the visible and near infrared bands (bands
1-5 and 7); the spatial resolution of ASTER 15 m for the visible and near-infrared bands. IKONOS
acquires data in 3 visible channels and NIR, with spatial resolution of 1-4 meters. ASTER and
IKONOS images are suggested to be included as soon as available, in addition to the Landsat. The
research includes fieldwork in-situ measurements of the seagrass distribution along the northern and
south-eastern coasts of Crete in chosen locations.\\
The optical measurements of the irradiance and radiance of the sea water and bottom cover types of
the seafloor have been received by the means of the optical sensors Trios-RAMSES Hyperspectral
UVA/UVB Irradiance Sensor and RAMSES-ARC Hyperspectral UV-VIS Radiance Sensor (Fig. \ref{fig:10}), both adjusted for the measurements of the irradiance and radiance (see Appendices: Tab. \ref{tab:18}, Tab. \ref{tab:19}).
The highest measured values are located in the diapason of 410-730 nm for the water irradiance (Fig. \ref{fig:49}) and 430-650 for the water radiance (Fig.\ref{fig:47}). 
Afterwards, the measured values of the
radiance and irradiance, respectively, have been used for the computation of the spectral reflectance
properties of the sea water and bottom cover types (Fig.\ref{fig:23}). The spectral range of radiance
cover diapason of 320-950 nm, and ittadiance measurements are covered in the interval of 280-500
nm, which is suitable for a characteristics of seagrass reflectance.
Different curves on the reflectance, radiance and irradiance graphs for example, on Fig.\ref{fig:43}, or \ref{fig:45}, enlarged) represent several series of
the measurements. The values of the spectral reflectance are received from the
computations of these values using Excel mathematical formulae. The graphs shown on Fig.\ref{fig:47}, Fig. \ref{fig:48}, Fig. \ref{fig:49} display values of the radiance and irradiance of the sea water in Agia Pelagia, with and without sediments and suspended particles, respectively. Graph on Fig \ref{fig:44} displays statistuical analysis of the measured sets of observations, i.e. shows the midspread of the statistical quartiles (Q1-Q3), mean and extreme values.

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.5]{GNU-17.jpg}
	\caption{Optical properties of the sea water with sediments, measured in aquarium tank. Agia Pelagia district, Crete}
	\label{fig:23}
\end{figure}
\pagebreak

@@

\begin{table}[htbp]
	\rowcolors{1}{LightSteelBlue}{Honeydew}
	\caption{Results of the statistical analysis of spectral reflectance of \textbf{P.oceanica}, with average values (for sets 1 - 350). Generalisation up to step 20 nm}
	\begin{center}
	\begin{tabular}{|c|c|c|c|c|c|c|}
	\hline
	Wavelength, nm & mean & Q1 & min & Q3 & max & median \\ \hline
		\textbf{318.23354} & 0.030467 & 0.038907 & 0.029764 & 0.069762 & 0.116100 & 0.048984 \\ \hline
		\textbf{338.29900} & 0.033560 & 0.043030 & 0.032847 & 0.076252 & 0.128290 & 0.054334 \\ \hline
		\textbf{358.37932} & 0.039897 & 0.051320 & 0.039131 & 0.091143 & 0.154409 & 0.066354 \\ \hline
		\textbf{378.47247} & 0.045786 & 0.058849 & 0.045039 & 0.105993 & 0.177150 & 0.078339 \\ \hline
		\textbf{398.57640} & 0.052346 & 0.066859 & 0.051625 & 0.122328 & 0.201038 & 0.091905 \\ \hline
		\textbf{418.68905} & 0.058942 & 0.074842 & 0.058240 & 0.138984 & 0.226028 & 0.106207 \\ \hline
		\textbf{438.80838} & 0.070690 & 0.089761 & 0.069999 & 0.167825 & 0.267712 & 0.130580 \\ \hline
		\textbf{458.93235} & 0.080107 & 0.102089 & 0.079392 & 0.191424 & 0.304933 & 0.149762 \\ \hline
		\textbf{479.05891} & 0.086278 & 0.110348 & 0.085546 & 0.207940 & 0.332934 & 0.162881 \\ \hline
		\textbf{499.18600} & 0.098498 & 0.126592 & 0.097689 & 0.239161 & 0.380603 & 0.188192 \\ \hline
		\textbf{519.31159} & 0.110222 & 0.143976 & 0.109022 & 0.265948 & 0.421370 & 0.210237 \\ \hline
		\textbf{539.43363} & 0.125694 & 0.166156 & 0.124310 & 0.302678 & 0.475842 & 0.240492 \\ \hline
		\textbf{559.55006} & 0.131844 & 0.175865 & 0.130257 & 0.319385 & 0.503907 & 0.253726 \\ \hline
		\textbf{579.65885} & 0.121915 & 0.166084 & 0.120186 & 0.302078 & 0.485661 & 0.237873 \\ \hline
		\textbf{599.75794} & 0.077236 & 0.111113 & 0.075669 & 0.200557 & 0.343876 & 0.154016 \\ \hline
		\textbf{619.84529} & 0.057038 & 0.085386 & 0.055588 & 0.154781 & 0.281737 & 0.117003 \\ \hline
		\textbf{639.91885} & 0.050841 & 0.077438 & 0.049432 & 0.141810 & 0.265181 & 0.106188 \\ \hline
		\textbf{659.97657} & 0.038118 & 0.059971 & 0.036997 & 0.110774 & 0.223366 & 0.082411 \\ \hline
		\textbf{680.01641} & 0.032892 & 0.052265 & 0.032012 & 0.095789 & 0.198389 & 0.071686 \\ \hline
		\textbf{700.03633} & 0.034756 & 0.058426 & 0.033643 & 0.101504 & 0.215413 & 0.075789 \\ \hline
		\textbf{720.03426} & 0.026287 & 0.047084 & 0.025162 & 0.082940 & 0.193535 & 0.061184 \\ \hline
		\textbf{740.00817} & 0.009740 & 0.022355 & 0.010145 & 0.042861 & 0.132244 & 0.029414 \\ \hline
		\textbf{759.95601} & 0.008651 & 0.020234 & 0.009191 & 0.039371 & 0.128165 & 0.026558 \\ \hline
		\textbf{779.87573} & 0.006019 & 0.014157 & 0.006397 & 0.028320 & 0.100314 & 0.019322 \\ \hline
		\textbf{799.76528} & 0.008607 & 0.020030 & 0.009050 & 0.037323 & 0.118123 & 0.026535 \\ \hline
		\textbf{819.62263} & 0.008777 & 0.020295 & 0.009288 & 0.037598 & 0.118055 & 0.026799 \\ \hline
		\textbf{839.44571} & 0.002562 & 0.008010 & 0.002864 & 0.017472 & 0.076515 & 0.011432 \\ \hline
		\textbf{859.23249} & 0.002653 & 0.006921 & 0.002897 & 0.016121 & 0.070377 & 0.009889 \\ \hline
		\textbf{878.98091} & 0.002327 & 0.008080 & 0.002821 & 0.018625 & 0.082462 & 0.011617 \\ \hline
		\textbf{898.68893} & 0.004077 & 0.013098 & 0.004709 & 0.031217 & 0.101146 & 0.019767 \\ \hline
		\textbf{918.35451} & 0.006215 & 0.020162 & 0.007229 & 0.045213 & 0.199711 & 0.029950 \\ \hline
		\textbf{937.97559} & 0.005783 & 0.026132 & 0.007307 & 0.065475 & 0.195072 & 0.040848 \\ \hline
		\textbf{951.03058} & 0.002296 & 0.026581 & 0.002380 & 0.067924 & 0.265845 & 0.041463 \\ \hline
	\end{tabular}
	\end{center}
	\label{tab:2}
\end{table}

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.30]{Fig-30.jpg}
	\caption{Main interface of WASI water color spectral simulation: \\ Spectral reflectance of \textit{P.oceanica} and silt at 0.5-4.0m}
	\label{fig:30}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\subfloat [Concentration of Gelbstoff at depths 0.5 – 8.0 m]{\label{fig:31a}\includegraphics[width=0.4\textwidth]{Fig-31a.jpg}}
	\subfloat [Bottom reflectance at depth 0.5-4.0 meters]{\label{fig:31b}\includegraphics[width=0.4\textwidth]{Fig-31b.jpg}}
	\caption{Sea water physical properties, modelled by WASI}
	\label{fig:31}
\end{figure}

\paragraph{Model parameters: depth and bottom cover fraction}
Although seagrass \textit{P.oceanica} can be found until depth limits down to 40 m depth (Hartog
1970), the most preferrable limits of its distribution in the Mediterranean Sea are shallow waters until
4 meters of depth.

\begin{table}
	\rowcolors{1}{Aquamarine}{Azure}
	\caption{Model-specific parameters of water WASI adjusted to simulate environment of the Mediterranean Sea along Crete}
	\centering
	 \begin{tabular}{|  p{2cm} | p{6cm} | p{25mm} | }
	    \hline
		    \textbf{Parameter, WASI} & \textbf{Name and description} & \textbf{Values} \\ \hline\hline
		    C-L & Concentration of large suspended particles & 8 \\ \hline
		   C(i), i=0..5 & Concentration of Phytoplankton & 0.035 -0.089 ug -l \\ \hline
		    bbS & Specific backscattering for small particles & 0.005 m2g-1 \\ \hline
		   T-W & Temperature of water & 17-25 °C \\ \hline
		    n & Exponent of Backscattering by small particles & 0.005 m2g-1 \\ \hline
		    Q &Anisotropy factor of upwelling radiation ("Q-factor") & 5.00 \\ \hline
		    sigma-L & Reflection factor of sky radiance & 0.0201 \\ \hline
		    b1 & Backscattering coefficient of saline waters & 0.00144 m-1 \\ \hline
		    λ0 & Reference Wavelength for Gelbstoff absorption & 440 \\ \hline
		    sun & Sun zenith angle & 45.0 \\ \hline
		    zB & Bottom depth & 4.00 \\ \hline
		   f(i), i=0...5 & Areal fraction of bottom surface type number n & 01/10/10 \\ \hline
		    K0 & Coefficient of Attentuation & 1.0546 \\ \hline
		   view & Viewing angle (0 = nadir) & 0\\ \hline
		    C-X & Concentration of non-chlorophyllous particles (absorption at λ0) & 0 \\ \hline
		   λS & Reference wavelength for scattering of small particles & 500 \\ \hline
		    C-S & Concentration of small suspended particles & 0 \\ \hline
		   S & Exponent of Gelbstoff absorption & 0.0140 \\ \hline
		    C-Y & Concentration of Gelbstoff (absorption at λ0) & 0.400 \\ \hline
		    Bn & BDRF of bottom reflectance (sand) & 0.318 sr -1\\
	    \hline
	  \end{tabular}
	   \label{tab:3}
\end{table}

@@

\paragraph{Spectral discrimination of \textit{P.oceanica}}
The patches of white sandy bottoms of the seafloor, studied in the fieldwork in Ligaria beach, are
much brighter than mattes of P.Oceanica ((Fig.\ref{fig:64}): seafloor types in Ligaria), which can be clearly seen
at the graph comparing values of the spectral reflectance of the carbonate sand (Fig.\ref{fig:65}) and that of P.
oceanica (Fig.\ref{fig:62}).
The graph is received in excel spreadsheet using mean values of spectral reflectances of
sand (Fig.\ref{fig:34}) and seagrass (Fig.\ref{fig:32}), respectively, which have been calculated from measurements of radiance and
irradiance received in Agia Pelagia bay.

@@

Finally we analysed 400 datasets made on two different data. 

@@

\begin{figure}
	\begin{center}
		\includegraphics[scale=0.45]{GNU-13.jpg}
		\caption{Multiplot of spectral reflectance of P.oceanica. Series 1-100. Shown midspread of the statistical quartiles Q1 and Q3 (vertical dashes) and
			mean value within the range (red bold dots). Gnuplot visualization­}
		\label{fig:35}
	\end{center}
\end{figure}
\begin{figure}
	\begin{center}
		\includegraphics[scale=0.5]{GNU-16.jpg}
		\caption{Multiplot of spectral reflectance of carbonate sand. Series 1-75. Shown midspread of the statistical quartiles Q1 and Q3 (vertical dashes) and
			mean value within the range (red bold dots). Gnuplot visualization­}
		\label{fig:36}
	\end{center}
\end{figure}

@@

\begin{table}[htbp]
	\rowcolors{1}{Ivory}{GhostWhite}
	\caption{Model summary of the \textit{regression} analysis: curve estimation and ANOVA table tested for single observations within one measurement set: spectral 			reflectance of \textbf{P.oceanica}. SPSS}
	\begin{center}
		\begin{tabular}{|c|c|c|c|}
			\hline\hline
			\textbf{R} & \textbf{R square} & \textbf{Adjusted R square} & \textbf{Std. Error of the Estimate} \\ \hline\hline
			.277 1 & .077 & .068126692 & .462 \\ \hline
		\end{tabular}
	\end{center}
	The independent variable is wavelength. 
	\label{tab:5}
\end{table}

\begin{table}[htbp]
	\rowcolors{1}{Ivory}{GhostWhite}
	\caption{\textit{ANOVA} table: exponential curve estimation in the regression analysis, tested for single observations within one measurement set: spectral reflectance of 		\textbf{P.oceanica}. SPSS}
	\begin{center}
		\begin{tabular}{|c|c|c|c| c|c|}
			\hline\hline
			& \textbf{Sum of squares} & \textbf{df} & \textbf{Mean Square} & F & Sig.\\ \hline\hline
			Regression & 1.810 & 1 & 1.810 & 8.477 & .004\\ \hline
			Residual & 21.781 & 102 & .214 & & \\ \hline
			Total & 23.592 & 103 & & & \\ \hline
		\end{tabular}
	\end{center}
	The independent variable is wavelength. 
	\label{tab:6}
\end{table}

\begin{table}[htbp]
	\rowcolors{1}{Ivory}{GhostWhite}
	\caption{Coefficients of the \textit{regression analysis} (exponential curve estimation) of the spectral reflectance of \textbf{P.oceanica}. SPSS}
	\begin{center}
		\begin{tabular}{| c | c | p{2cm}| c | c | c |}
			\hline\hline
			& \multicolumn{2}{|c|}{Unstandardized Coefficients}\\
			\cline{2-3}
			& B & Std.Error & Stand. Coef. Beta & t & Sig.\\ \hline\hline
			wavelength & -.001 & .000 & -.277 & -2.912 & .004 \\ \hline
			constant & .464 & .121 & & 3.821 & .000 \\ \hline
		\end{tabular}
	\end{center}
	The underlying process assumed is independence (white noise).\\
	 Based on the asymptotic chi-square approximation.
	\label{tab:7}
\end{table}
\pagebreak
